Differences from our PPoPP Conference Paper \cite{KBP16}

### 2018-09-06 latex/toms/experiments.tex
fixed tex compilation errors (beware, first compilation takes a very long time, but subsequent ones aren't bad)
change 129 to 162 for synthetic

%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{4.9}
\begin{subfigure}{0.3 \columnwidth}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
\subcaption{Low rank $k=32$}
\label{fig:accuracylr81k32}
\end{subfigure}
~
\begin{subfigure}{0.3 \columnwidth}
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
\subcaption{Low rank $k=64$}
\label{fig:accuracylr81k64}
\end{subfigure}
~
\begin{subfigure}{0.3 \columnwidth}
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
\subcaption{Low rank $k=96$}
\label{fig:accuracylr81k96}
\end{subfigure}

\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Low Rank Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid.}
\label{fig:convergencelowrank}
\end{figure}

%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{9.9}
\begin{subfigure}{0.3 \columnwidth}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
\subcaption{Low rank $k=32$}
\label{fig:accuracylr81k32}
\end{subfigure}
~
\begin{subfigure}{0.3 \columnwidth}
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
\subcaption{Low rank $k=64$}
\label{fig:accuracylr81k64}
\end{subfigure}
~
\begin{subfigure}{0.3 \columnwidth}
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
\subcaption{Low rank $k=96$}
\label{fig:accuracylr81k96}
\end{subfigure}

\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid.}
\label{fig:convergenceuniform}
\end{figure}

@@

\begin{subfigure}{0.45 \columnwidth}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\nogpu}{0}
\cpuvsgpuplot
\end{tikzpicture}
\ylabelfalse
\subcaption{CPU}
\label{fig:cpulr81}
\end{subfigure}
~
\begin{subfigure}{0.45 \columnwidth}
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\nogpu}{1}
\cpuvsgpuplot
\end{tikzpicture}
\subcaption{GPU}
\label{fig:gpulr81}
\end{subfigure}
~
\caption{Timing comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Low Rank Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:cpuvsgpulowrank}
\end{figure}

@@

\begin{subfigure}{0.45 \columnwidth}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\cpuvsgpuplot
\end{tikzpicture}
\ylabelfalse
\subcaption{CPU}
\label{fig:cpuuni81}
\end{subfigure}
~
\begin{subfigure}{0.45 \columnwidth}
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\nogpu}{1}
\cpuvsgpuplot
\end{tikzpicture}
\subcaption{GPU}
\label{fig:gpuuni81}
\end{subfigure}
~
\caption{Timing comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:cpuvsgpuuniform}
\end{figure}

\renewcommand{\numiterations}{29}
\begin{figure}
\begin{subfigure}{0.45 \columnwidth}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/lucuni81pksweep.csv}
\lucplot
\end{tikzpicture}
\ylabelfalse
\subcaption{Uniform}
\label{fig:lucuni81}
\end{subfigure}
~
\begin{subfigure}{0.45 \columnwidth}
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/luclr81pksweep.csv}
\renewcommand{\nogpu}{1}
\lucplot
\end{tikzpicture}
\subcaption{Low Rank}
\label{fig:luclr81}
\end{subfigure}
~
\caption{LUC comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform and Low Rank Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:luccomp}
\end{figure}

>>>>

%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{4.9}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Low Rank Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid.}
\label{fig:convergencelowrank}
\end{figure}

\begin{figure}
%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{9.9}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid.}
\label{fig:convergenceuniform}
\end{figure}

@@

\subfloat[CPU \label{fig:cpulr81}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\nogpu}{0}
\cpuvsgpuplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[GPU \label{fig:gpulr81}]{
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\nogpu}{1}
\cpuvsgpuplot
\end{tikzpicture}
}
\caption{Timing comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Low Rank Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:cpuvsgpulowrank}
\end{figure}

@@

\subfloat[CPU \label{fig:cpuuni81}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\cpuvsgpuplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[GPU \label{fig:gpuuni81}]{
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\nogpu}{1}
\cpuvsgpuplot
\end{tikzpicture}
}
\caption{Timing comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:cpuvsgpuuniform}
\end{figure}

\renewcommand{\numiterations}{29}
\begin{figure}
\subfloat[Uniform \label{fig:lucuni81}]{
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/lucuni81pksweep.csv}
\lucplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low Rank \label{fig:luclr81}]{
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/luclr81pksweep.csv}
\renewcommand{\nogpu}{1}
\lucplot
\end{tikzpicture}
}
\caption{LUC comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov on 4D Synthetic Uniform and Low Rank Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid on CPU.}
\label{fig:luccomp}
\end{figure}
